\section{Sales Forcasts}

The actual entity being sold in this business is the advertising space on the web site.  The value of this space is directly proportional to the number of visitors to the site that view the advertisments.  Hence this section concentrates on \emph{page views}, that is the number of pages of the site viewed by the visitors.

To get an idea of the number of people we can expect to visit the site we contacted the maintainers of several other internet sites to ask them for their visitor figures.  The sites contacted were all sites that we believe that our target audience may also visit, this was to get an idea of the popularity of the sites in this sector.

The first two people contacted were the maintainers of the FreeBSD and Debian Linux web sites.  Both of these web sites have mailing list archives that can be browsed and searched (with limited capability).

\begin{table}[!htb]
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Site & Search & Search + Browse \\
\hline
FreeBSD  &  51,000 & 255,000 \\
Debian Linux & 24,000 & - \\
\hline
\end{tabular}
\caption{Page views per month}
\end{center}
\end{table}

In the case of FreeBSD we found that 51,000 page views per month purely for the search page.  However, including browsing the messages and viewing the messages returned by the search results, results in 255,000 page views per month.  This means that for each for each visitor they view on average 5 pages.  If there is one advert per page, this means that there will be 5 \emph{impressions} of an advertisment per visitor.

If these figures are extrapolated using the percentages found in Section \ref{sec:size}, which show BSD to be about 10\% of the Open Source sector, that results in 2.5 million page views per month.  In fact BSD is a term describing three projects FreeBSD, NetBSD and OpenBSD, and we have only used the numbers for FreeBSD as a base figure.  FreeBSD has the largest share of the three BSDs but this means that the potential market may be higher.

We are aiming to reach the growth phase by 6 months and occupy a 10\% market share by the end of the first year.  This means attracting 250,000 page views a month.  We feel this is an appropriate target based upon the positive reaction from the survey we carried out, detailed in Section \ref{sec:survey}.

The reachability of this target is strengthened by the statistics from a new news site, \emph{Daily Daemon News}, relating specifically to BSD news.  The site has been running for six months and, on contacting the author, we found that the site has grown from an initial 75,000 to 200,000 page views per months in that time.


%According to the FreeBSD mailing list administrator, there are 1,750 subscribers to the most popular list \texttt{freebsd-current} and 1,500 to the next popular \texttt{freebsd-questions} these lists roughly correspond to the developer and the novice user sectors respectively, although there is probably quite a large overlap.

%Etherworks has been keeping archives of around 120 mailing lists for the past year, since the idea was conceived.  These archives are not processed in any way and are just stored on disk for later loading into the search system.

%So far in these archives there are over 51,000 distinct senders to the lists.  If we then assume that 

