%% $Id: require.tex,v 1.8 2000/05/08 16:21:12 matt Exp $

\chapter{User Requirements}
\label{require}
\section{The Customer}
Etherworks, a startup, Bristol based company has been formed by the
author and several University of Bristol graduates.  The aim of the
company is to setup a web based archive of Open Source Software
\cite{www:opensource} electronic mailing lists.  The founders of the company 
have collectively put up the money for capital.  So far this capital has been used to purchase a server to develop and host the archive on.  Revenue is expected to be generated via advertising on the site once it is established.

The work completed for this project will comprise mainly of the backend systems to operate the archive.  The other members of Etherworks will be working on the web site design, graphics and administrative tools.  These are not to be considered as part of this project.

\section{Motivation}
Much of the development of Open Source software is discussed on mailing
lists.  There are hundreds of these lists covering various topics to do
with the use and development of the software.  The main essence of
Open Source software is communication between the community developing the
software.  

Most of these lists are not archived in any way, and the
archives that do exist only offer very basic searching and browsing
functions.  Due to the computationally expensive nature of searching
through large archives, most of the archives only allow the user to search
through a single subsection at a time.

Many of the questions asked on the lists have often been previously asked,
and more importantly answered.  What is needed is a single central archive
of the various lists, which users can search through to find what they are
looking for.

This site has the potential to be a very valuable resource used by
both developers and users of all levels.

Nothing like this at this scale currently exists on the internet.
There are quite a few smaller sites that archive multiple lists, but
none with a site-wide search facility.

Many web search engines, such as AltaVista and Infoseek,  also sell
their indexing and search software as a separate standalone commercial
product.  However this software is geared towards indexing web sites
and not mailing lists.

\section{Requirements}
In order to set this archive apart from other similar sites on the net
it will have to offer much larger capacity and more advanced features:

\subsection*{Capacity}
The archive will have to be able to handle the storage, retrieval,
and searching of millions of messages.  It must be capable of handling 
several simultaneous users a second visiting the site without
significant slowdown.

\subsection*{Scalability}
As the service become more popular and the load increases, it should be  
possible to split the components of the archive up to run on seperate
servers.  This should increase the capacity that can be handled by the
archive.

\subsection*{Near Real-Time}
The archive must make messages available for browsing as soon as they
arrive.  The search indexes must be updated regularly, at least once a 
day, so that searches return recent messages. 

\subsection*{Browsing}
Users must be able to easily and efficiently browse the archive and
see the most recently sent messages of a particular list.  They must
be able view the individual messages and move to next and previous
messages in the message's thread. 

\subsection*{Searching}
The site must allow users to search through the archives of messages
for keywords. They must be able to search across all lists held or
just a select set of lists.  The results must be ranked by relevance
and must be returned within a couple of seconds.

\subsection*{Customisation}
The site must be customisable by the users.  They must be able
personalise various aspects of the site, such as default searches,
time and date formats, number of messages per screen to show.

\subsection*{Cost}
Etherworks are supplying a server to develop the site and software
on.  The server should be sufficient to run the full site once opened
to the public for the first couple of months.  The only major cost
anticipated will be the cost of co-locating the server at an ISP once
the site goes commercial.

\subsection*{Advertising Space}
The site is expected to generate revenue through advertisements placed on the 
site.  Therefore the site must be designed in such a way to accommodate various standard sized banner ads.

% LocalWords:  Etherworks Opensource internet AltaVista Infoseek co ISP
